Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-04-23 scripts/03_clustering.Rmd
Fixing silhouette scores + speed ups

```{r}
possible_n_clusters = 5:20

@@

```{r elbow_method}

# function to compute total within-cluster sum of square 
within_cluster_sum_of_squares = function(n_cluster){
    return(moanin:::splines_kmeans(y, splines_model,
				   n_clusters=n_cluster, random_seed=42,
				   n_init=10)$tot.withinss)
}

i = 0
wss_values = list()
for(n_cluster in possible_n_clusters){
    wss_values[i] = within_cluster_sum_of_squares(n_cluster)
    i = i + 1
}

plot(possible_n_clusters, wss_values,
     type="b", pch=19, frame=FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")

@@

```{r average_silhouette_method}
# function to compute average silhouette for k clusters
average_silhoutte = function(n_cluster) {
    skmeans_results = moanin:::splines_kmeans(
	y, splines_model, n_clusters=n_cluster,
	random_seed=42, n_init=10)
    silhouette_results = cluster::silhouette(skmeans_results$cluster, dist(y))
    return(mean(silhouette_results[, 3]))
}

# extract the average silhoutte
average_silhoutte_values = list()
i = 1
for(n_cluster in possible_n_clusters){
    average_silhoutte_values[i] = average_silhoutte(n_cluster)
    i = i + 1
}

plot(possible_n_clusters, average_silhoutte_values,
     type="b", pch=19, frame=FALSE,
     xlab="Number of clusters K",
     ylab="Average Silhouettes")
```

>>>>

```{r running_clustering_on_all_k}
all_possible_n_clusters = c(5, 7, 9, 11)
all_clustering = list()
wss_values = list()

i = 1
for(n_cluster in all_possible_n_clusters){
    clustering_results = moanin:::splines_kmeans(
	y, splines_model,
	n_clusters=n_cluster, random_seed=42,
	n_init=10)
    wss_values[i] = sum(clustering_results$WCSS_per_cluster)
    all_clustering[[i]] = clustering_results$clusters
    i = i + 1
}
```

@@

```{r elbow_method, fig.width=6, fig.height=4}

# function to compute total within-cluster sum of square

plot(all_possible_n_clusters, wss_values,
     type="b", pch=19, frame=FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")

@@

```{r average_silhouette_method, fig.width=6, fig.height=4}
# function to compute average silhouette for k clusters
average_silhouette = function(labels, y) {
    silhouette_results = cluster::silhouette(unlist(labels[1]), dist(y))
    return(mean(silhouette_results[, 3]))
}

# extract the average silhouette
average_silhouette_values = list()
i = 1
for(i in 1:length(all_clustering)){
    labels = all_clustering[i]
    average_silhouette_values[i] = average_silhouette(labels, y)
    i = i + 1
}

plot(all_possible_n_clusters, average_silhouette_values,
     type="b", pch=19, frame=FALSE,
     xlab="Number of clusters K",
     ylab="Average Silhouettes")
```

### 2019-04-23 scripts/04_downstream_analysis.Rmd
Fixing silhouette scores + speed ups

```{r enrichment_analysis, results="hide", message=FALSE}
clusters = sort(as.vector(unlist(unique(labels))))
clusters = c(1, 2, 3)
all_pathways = data.frame()
for(cluster in clusters){
    genes = gene_names[labels == cluster]

@@

@@

```{r go_term_enrichment, results="hide", message=FALSE}

cluster = c(1, 2, 3)
ontologies = c("BP", "NF", "CC")
# It's taking too long to compile with everything. Just limit ourselves for
# now to BP
ontologies = c("BP")
all_go_terms = data.frame()
for(cluster in clusters){
    for(ontology in c("BP", "NF", "CC")){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping)

@@

>>>>

```{r enrichment_analysis, results="hide", message=FALSE, eval=FALSE}
clusters = sort(as.vector(unlist(unique(labels))))
all_pathways = data.frame()
for(cluster in clusters){
    genes = gene_names[labels == cluster]

@@

```{r echo=FALSE}
all_pathways = read.table("results/all_pathways.tsv",
			  sep="\t")
```

@@

```{r go_term_enrichment, results="hide", message=FALSE, eval=FALSE}

ontologies = c("BP")
all_go_terms = data.frame()
for(cluster in clusters){
    for(ontology in ontologies){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping, ontology=ontology)

@@

```{r echo=FALSE}
all_go_terms = read.table(
    "results/all_go_terms.tsv",
    sep="\t")
```
